\documentclass[letterpaper,12pt]{article}
\usepackage{amsfonts,amsmath,amssymb,fancyhdr,datetime}

\usepackage[pdftex]{graphicx} % Great for including graphics
\usepackage{wrapfig}          % Wrapper for figures

\usepackage{upquote}
\usepackage{verbatim}

% Relies on the datetime package to reformat the date the way I like.
\newdateformat{iaindateformat}
              {\THEYEAR\hspace{.5em}\monthname[\THEMONTH]\hspace{.5em}\THEDAY}
\iaindateformat

\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.5in

\topmargin 0.0in
\headheight 1.0in
\textheight 9.0in

\renewcommand{\choose}[2]{\genfrac{(}{)}{0pt}{}{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\thesection}{\arabic{section}}

\pagestyle{fancy}
  \setlength\headheight{14.5pt}
  \renewcommand{\headrulewidth}{0.4pt}
  \renewcommand{\footrulewidth}{0.4pt}
  \fancyhead[R]{\bf Developer \thepage}
  \fancyhead[L]{\bf }
  \fancyfoot[R]{\bf Generated: \today\hspace{.5em}\currenttime}
  \fancyfoot[L]{\bf Community Bridge}
  \fancyfoot[C]{\bf \thepage}
\setlength{\parindent}{0pt} 
\setlength{\parskip}{0.5em} 
\begin{document}
  \section{Overview}
  Throughout this document, the term ``web application'' is used. The web
  application can be any forum, CMS, blogging software, etc. that uses MySQL for
  its database.
  
  These are the major features of Community Bridge:
  \begin{enumerate}
    \item Minecraft player to web application user ``linking''.
    \item Group synchronization (currently a misnomer, since the
          ``synchronization'' is only one way)
    \item Recording statistical information about the players in web
          application custom fields.
    \item Kicking of players who are banned from the web application.
  \end{enumerate}
  
  The first of the features is essential, without it, none of the other
  features of the plugin would work. Given that the linking feature's
  importance, it is the first thing to evaluate when ensuring that
  CommunityBridge is operating correctly.

  \clearpage
  \subsection{config.yml Preamble and General Settings Section}
  \verbatiminput{config-preamble.txt}

  \clearpage
  \section{Database Handling}
  The config.yml section contains the hostname, port, database name, username,
  and password. It should correctly notify the server owner if the database
  information is incorrect or correct.
  
  \clearpage
  \subsection{config.yml Database Section}
  \verbatiminput{config-database.txt}

  \clearpage
  \section{Linking Feature}
  For each of the following configurations, CB should:
  \begin{itemize}
    \item Recognize a player as not being registered, e.g., not present in the
    web application's database.
    \item Correctly identify a player as being registered--identifying the
    correct user.
    \item If kick-unregistered is turned on, kick unregistered players.
  \end{itemize}

  Possible Configurations (order of complexity):
  \begin{itemize}
    \item Minecraft playername and web application username are required to be
      the same. Required information: users table, user id column,
      username/playername column.
    \item Minecraft playername and web application username can be different;
      the Minecraft playername is in a separate column on the users table.
      Required information: users table, user id column, username/playername
      column.
    \item Minecraft playername and web application username can be different;
      the Minecraft playername is on a different table in its own column
      (frequently, this is because it is implemented through a custom profile
      field in the web application). Required information: tablename, user id
      column, username/playername column.
    \item Minecraft playername and web application username can be different;
      the Minecraft playername is on a different table that data is stored in
      the key-value format. Required information: tablename, user id column,
      key column, value column, data key name.
  \end{itemize}

  Fortunately, the overall result is the first three possible configurations
  require the same information. Only when the minecraft playername is stored in
  a key-value pair do we need different information.
  
  \clearpage
  
  \subsection{config.yml Section for Linking Feature}
  \verbatiminput{config-linking-feature.txt}
  
  \subsection{messages.yml Section for Linking Feature}
  Messages related to the linking feature in the messages.yml.
  \verbatiminput{message-linking-feature.txt}

  \clearpage
  \section{Authentication}
  \begin{itemize}
    \item {\bf (NYI)} If authentication is off {\bf DO NOT} force authentication.
    \item {\bf (NYI)} If authentication is on, handle a valid authentication by...
    \item {\bf (NYI)} If authentication is on, respond to an failed authentication attempt by...
  \end{itemize}
  \subsection{Proposed config.yml Section}
  \verbatiminput{config-authentication-feature.txt}
  \clearpage
  \section{Group Synchronization}
  Many web applications have a notion of a primary group. In fact, some only
  allow a member to have membership in a single group.

  On the other hand, permissions systems appear to rarely have a notion of a
  primary group. In addition, they frequently have per-world settings, so the
  world name must be included any operations with a permissions system.

  Possible configuration types for a ``primary'' group includes:
  \begin{itemize}
   \item A ``primary'' group\_id stored on a table alongside a user\_id. Required
    information includes: table\_name, user\_id column, group\_id column.
   \item A ``primary'' group\_id stored in a key-value pair. Required information
    includes: table\_name, user\_id column, key column, value column, data key name
  \end{itemize}

  Possible configuration types for ``secondary'' group includes:
  \begin{itemize}
   \item A list of ``secondary'' group IDs stored in a single field alongside a
    user\_id. Required information includes: table\_name, user\_id column,
    group\_ids column, group\_id delimiter.
   \item A junction table to create the many-to-many relationship between
    user IDs and group IDs. Required information includes: table\_name, user\_id
    column, group\_id column.
   \item A series of key-value pairs on a key-value table. Required information
    includes: table\_name, user\_id column, key volumn, value column, data key name
  \end{itemize}


	\clearpage
  \subsection{Proposed config.yml Section}
  \verbatiminput{config-group-synchronization.txt}
  
  \clearpage
  \subsection{Proposed messages.yml Section}
  \verbatiminput{message-group-synchronization.txt}

  \clearpage
  \appendix
  \section{Full Proposed config.yml}
  \verbatiminput{config-preamble.txt}
  \verbatiminput{config-database.txt}
  \verbatiminput{config-linking-feature.txt}
  \verbatiminput{config-group-synchronization.txt}

  \clearpage
  \section{Full Proposed messages.yml}
  \verbatiminput{message-linking-feature.txt}
  \verbatiminput{message-group-synchronization.txt}
\end{document}
